---
title: "ochre_intro"
author: "PARDaHlotE"
date: "26 October 2017"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{ochRe}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(fig.width = 7, echo = FALSE)
library(ochRe)
library(dichromat)
library(colorspace)
library(elevatr)
```

# Introduction

"Welcome to all people... To this land of ochre" - Ruby Hunter

The [**ochre**](CRAN link?) package contains colour palettes inspired by the Australian landscape, iconic Australian artists and images. 

# Installation

``` r
install.packages("ochRe")
```

**Or the development version**

``` r
devtools::install_github("ropenscilabs/ochRe")
```

# ochRe palette choices

The package contains sixteen colour palettes.


```{r use_names, echo=TRUE}

# See names of all palettes
names(ochre_palettes)
```

```{r see_palettes, fig.height = 8}
pal_names <- names(ochre_palettes)

par(mfrow=c(length(ochre_palettes)/2, 2), lheight = 2, mar=rep(1, 4), adj = 0)
for (i in 1:length(ochre_palettes)){
    viz_palette(ochre_palettes[[i]], pal_names[i])
}
```


## Colour vision impairment
These plots show how each of the palettes perform for different types of colour vision impairment (using dichromat). Palettes that perform best are "galah", "namatjira", "williams_pilbara", and "healthy_ _reef"  

### Green-Blind (Deuteranopia)
```{r dichromate_deat, fig.height = 5}
par(mfrow=c(length(ochre_palettes)/2, 2), lheight = 2, mar=rep(1, 4), adj = 0)
for (i in 1:length(ochre_palettes)){
    viz_palette(dichromat(ochre_palettes[[i]], "deutan"), pal_names[i])
}
```


### Red-Blind (Protanopia)
```{r dichromate_protan, fig.height = 5}
par(mfrow=c(length(ochre_palettes)/2, 2), lheight = 2, mar=rep(1, 4), adj = 0)
for (i in 1:length(ochre_palettes)){
    viz_palette(dichromat(ochre_palettes[[i]], "protan"), pal_names[i])
}
```


### Blue-Blind (Tritanopia)
```{r dichromate_tritan, fig.height = 5}
par(mfrow=c(length(ochre_palettes)/2, 2), lheight = 2, mar=rep(1, 4), adj = 0)
for (i in 1:length(ochre_palettes)){
    viz_palette(dichromat(ochre_palettes[[i]], "tritan"), pal_names[i])
}
```


### Desaturated
```{r desaturate, fig.height = 5}
par(mfrow=c(length(ochre_palettes)/2, 2), lheight = 2, mar=rep(1, 4), adj = 0)
for (i in 1:length(ochre_palettes)){
    viz_palette(desaturate(ochre_palettes[[i]]), pal_names[i])
}
```

# Usage

The ochRe package contains color scale functions for **ggplot**
plots: `scale_color_ochre()` and `scale_fill_ochre()`. 

Here the `olsen_qual` is used for a scatter plot of `mtcars` data.

```{r mtcars, echo = TRUE, message = FALSE}
library(tidyverse)

ggplot(mtcars, aes(mpg, wt)) + 
   geom_point(aes(colour = factor(cyl))) + 
   scale_colour_ochre(palette="olsen_qual")
```

This code uses the `winmar` palette is used for a scatter plot of `mpg` data

```{r mpg, echo = TRUE, message = FALSE}
ggplot(data = mpg) + 
   geom_point(mapping = aes(x = displ, y = hwy, color = class)) +
   scale_colour_ochre(palette="winmar")
```

Here the default palette `namatjira_qual` is used in a stacked bar chart using the `diamonds` data. 
```{r diamonds, echo=TRUE, message=FALSE}
 ggplot(diamonds) + geom_bar(aes(x = cut, fill = clarity)) +
   scale_fill_ochre()

```


```{r maps, echo=TRUE, message=FALSE, fig.height=8}
load("../data/oz_elev.rda")
library(elevatr)
library(raster)
par(mfrow=c(6, 3))
for (curCol in ochre_palettes%>%names()){
    colpal <- ochre_pal(palette = curCol)(150)
    ex <- extent(110, 155, -45, -10)
    elev <- raster::crop(elev, ex)
    elev[elev < 0] <- NA
    topo <- list(x = xFromCol(elev), y = rev(yFromRow(elev)), 
                    z = t(as.matrix(elev))[, nrow(elev):1])
                     par(mar = rep(0, 4), bg = "#444444")
    image(topo, useRaster = TRUE, col = colpal,
       axes = FALSE, xlab = "", ylab = "",
             asp = cos(27.5 * pi/180))

}
                 
par(mfrow=c(1,1))
```

## Palette inspiration

### namatjira_qual and namatjira_div

These palettes are based on the painting "Twin Ghosts",  by Albert Namatjira. Each palette has eight colours.

http://www.menziesartbrands.com/sites/default/files/field/catalogue_items//DM_24017.jpg


### mccrea

This palette is based on the painting "Melbourne, Collins St", 1841, by Georgiana McCrae. 
It has eleven colours.   

https://upload.wikimedia.org/wikipedia/commons/c/c0/Melbourne_Collins_Street_1841.jpg

### parliament

This palette is based on based on the tapestry in the Great Hall of Parliament House, of a landscape by Arthur Boyd - Untitled (Shoalhaven Landscape), 1984, as well as the colours of the and House of Representatives and the Senate. 
It has eight colours.   

https://www.aph.gov.au/~/media/06%20Visit%20Parliament/66%20Parl%20House%20Art%20Collection/661%20five%20treasures/five%20treasures%20detail%20pics/M19840057UntitledBOYDunframed.png?la=en)
  
Parliament House:
https://www.peo.gov.au/learning/closer-look/australias-parliament-house/a-place-for-the-parliament.html  

### tasmania
This palette is based on colours in the bay of fires and cradle mountain.
It has seven colours.

### nolan_ned
This palette is based on the painting "Ned Kelly", 1946, by Sidney Nolan.
It has five colours.

https://cs.nga.gov.au/images/lrg/28926.jpg

### winmar
This palette is based on a photograph by Wayne Ludbey, "Nicky Winmar St Kilda Footballer", 1993. It has seven colours.

https://nga.gov.au/federation/Large/27707.jpg

### olsen_qual and olsen_div
These palettes are based on the painting "Sydney Sun", 1965, by John Olsen. olsen_qual has six colours, olsen_div has 14 colours.

https://artsearch.nga.gov.au/images/lrg/26102.jpg


### williams_pilbara
This palette is based on the painting "Mount Nameless (morning)", 1981, by Fred Williams. The palette has seven colours. 

http://www.art-almanac.com.au/wp-content/uploads/2013/11/benalla_mt_nameless_review_1213.jpg


### healthy_reef
This palette is based on colours of the great barrier reef. The palette has nine colours. 

http://aussiedestinationtours.com/wp-content/uploads/2014/07/Greatbarrierreef.jpg 

### emu_woman_paired
This palette is based on the painting "Emu Woman", 1988–89, by Emily Kame Kngwarreye, The palette has eighteen colours. 

http://www.nma.gov.au/__data/assets/image/0003/225939/88_Emu_Woman_w480.jpg

### galah
This palette is based on the colours of the galah. It has five colours.  

https://images.theconversation.com/files/138409/original/image-20160920-18705-aaufc.jpg?ixlib=rb-1.1.0&q=45&auto=format&w=754&fit=clip 

### lorikeet
This palette is based on the colours of the rainbow lorikeet. It has six colours.  

http://reptilepark.com.au/wp-content/uploads/2015/11/birds_rainbow_lorikeet2.jpg

### dead_reef
This palette is based on the colours a bleached barrier reef. It has six colours.  

http://cdn.newsapi.com.au/image/v1/7c2f433cd1e020a6ad1b7018070c55a6 

### jumping frog
This palette is based on "Jumping Frog", c1982 by John Olsen. It has five colours.  

http://cdn.artserieshotels.com.au/images/made/images/remote/http_cdn.artserieshotels.com.au/images/uploads/main/john-olsen-artist-artwork1_600_400_60.jpg

